Scope - Does not include pegging, does not include knowledge of whose crib it currently is. 
        Just what is likely to score the highest number of points in that hand
      - Does say what the lowest possible (usually but not always 4-card hand only), highest possible (eg got the best cut), and average (expected) points per hand. 
        Keeps track of which cuts give the highest floor, highest ceiling, and highest average
      - Should average be mean or median? Mean is easier to keep track of and follows EV more closely so I'll do that. 


Should card be a class
 - Yes. It has a face (important for runs), a value (importatn for 15s and differnt for JQK), and a suit (important for flushes and rouges)
 - Face is an int (JQK -> 11, 12, 13), value is an int and suit could be a char or an int (DHSC -> 0123)

Finding the value of a given hand:
 - You need four cards and a cut to make a valid hand. Which is which matters for the rouge. The cut is inaccessible before throwing out
 - Sort the cards and get all of the subsequences of length 2 or above (can rip this from a09 with some slight tweaks). 
        This includes the cut, so it would be a subsequencer of length 5, all sorted
 - Tweaks necessary for a09: Subsequencer should accept Cards, not Integers, Subsequencer should put things into a List<List<Cards>>
        Need an iterator for the List<List<Cards>> to see of those subsequences score
 - If any subsequence of cards' values adds to 15, add 2.
 - If any subsequence of length 3 or above is a run, considering card faces, add points corresponding to the length

Deck is also a class, possibly private in card. It's made up of all 52 cards, and can either regen or shuffle

Hand consists of 5 randomly chosen cards from Deck. If Deck is shuffled, can just take the last 5 cards off of Deck

Scoring a hand: ROUGE and FLUSH must be checked before searching for RUNS and PAIRS
              : Check ROUGE first, by checking through the whole hand for (face == 11 and (card.suit == cut.suit))
                    - There may be more than one jack in the hand and the hand isn't yet sorted so you have to go through all 4
              : After checking for ROUGE, check for 4-FLUSH. 
                    - If 4-FLUSH, check for 5-FLUSH
              Then check for RUNS

Checking for RUNS: Sort the Cut and the Hand together. Get them all together and check if the 5-card hand is a run.
                   - If it is, longestRun = 5. If not, check all subsequences of length 4, and see if any of them are runs, and the same for length 3. 
                   - Once we know the longest run, get all subsequences of exactly that length, and count Length number of points 

Subsequencing option (faster but cruder): hard-code all 20 subsequences with length >= 2 for an array of length 5.
                                          also has 10 subsequences with length >= 3
                                          
For 15s there's nothing else, but for runs you can stop if finding a run of 4 or 5
